Country-Level Impact of Education on Entrepreneurship

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

### What we intend to do

**Quantitative Analysis of the Impact of Education on Entrepreneurship**

*Research Design*

At this stage, having explained how determinants of entrepreneurship have been looked into, having mentioned how education has been related to entrepreneurship so far, we need to assert here our very research design. What we expect to find out is to what extent the support of students' self-confidence within the education system impacts the rate of entrepreneurship across OECD countries.

@@

The support of students' self-confidence within education systems as we just defined it can also affect the students' entrepreneurial self-efficacy, that should be controled for. To do so, we will look at average perceived entrepreneurial capabilities and fear of failure in starting a business across the population at the country-level.

@@

The lack of suitable data as well as the fact that OECD PISA tends to focus on different aspects of education systems for every triennal survey, lead us to give up on this for the time being. But we still think that should be included in a future research on that topic.

>>>>

***Quantitative Analysis of the Impact of Education on Entrepreneurship***

**Research Design**

At this stage, having explained how determinants of entrepreneurship have been looked into, having mentioned how education has been related to entrepreneurship so far, we need to assert here our very research question which is:

To what extent does the support of students' self-confidence within the education system impacts the rate of entrepreneurship across OECD countries?

@@

The support of students' self-confidence within education systems as we just defined it can also affect the students' entrepreneurial self-efficacy, that should be controled for. To do so, we will look at the average perceived entrepreneurial capabilities and fear of failure in starting a business across the population at the country-level.

@@

The lack of suitable data as well as the fact that OECD PISA (Programme for International Student Assessment) tends to focus on different aspects of education systems for every triennal survey, lead us to give up on this for the time being. But we still think that should be included in a future research on that topic.
